Localisation and Sensor Privacy Using the Extended Information Filter and Private Linear-Combination Aggregation\thanksref{footnoteinfo}

### 2020-08-28 main.tex
Appendix comment
Encoding started but ran into problem - code used Farohki encoding, but when writing up the generalised version realised that this is simply an overcomplication of straightforward quantisation mod N - will update code to use simpler quantisation method, and update here when that and the new plots work More big comments

@@

@@

\subsection{Notation}
Notation

@@

\section{Private Localisation Preliminaries}

\subsection{Integer Encoding for Real Numbers}
Point out the integer range limit introduced by our scheme, $x<N$, for both the weights and the values.

@@

@@

\subsection{Requirements for Measurement Model}

@@

@@

@@

% Each appendix must have a short title.
% Sections and subsections are supported
% in the appendices.
\appendix
\section{Indistinguishability under Chosen Plaintext Attack (IND-CPA)} \label{app:ind_cpa}
A public-key encryption scheme is defined by the tuple of algorithms $(\mathsf{Setup}, \mathsf{Enc}, \mathsf{Dec})$, defined as
\begin{description}
    \item[$\mathsf{Setup}(\kappa)$] On input of security paramater $\kappa$, generate public key $pk$ and secret key $sk$
    \item[$\mathsf{Enc}(pk, x)$] Encryption of value $x$ is computable using the public key $pk$, obtaining $\mathcal{E}_{pk}(x)$.
    \item[$\mathsf{Dec}(sk, \mathcal{E}_{pk}(x))$] Decryption of value $x$ is computable using the secret key $sk$.
\end{description}

>>>>

% 
% 8888888          888                    
%   888            888                    
%   888            888                    
%   888   88888b.  888888 888d888 .d88b.  
%   888   888 "88b 888    888P"  d88""88b 
%   888   888  888 888    888    888  888 
%   888   888  888 Y88b.  888    Y88..88P 
% 8888888 888  888  "Y888 888     "Y88P"  
%                                         
%                                         
%                                         
%

@@

% 
% ##       #### ######## 
% ##        ##     ##    
% ##        ##     ##    
% ##        ##     ##    
% ##        ##     ##    
% ##        ##     ##    
% ######## ####    ##    
%

@@

% 
% ##    ##  #######  ########    ###    ######## ####  #######  ##    ## 
% ###   ## ##     ##    ##      ## ##      ##     ##  ##     ## ###   ## 
% ####  ## ##     ##    ##     ##   ##     ##     ##  ##     ## ####  ## 
% ## ## ## ##     ##    ##    ##     ##    ##     ##  ##     ## ## ## ## 
% ##  #### ##     ##    ##    #########    ##     ##  ##     ## ##  #### 
% ##   ### ##     ##    ##    ##     ##    ##     ##  ##     ## ##   ### 
% ##    ##  #######     ##    ##     ##    ##    ####  #######  ##    ## 
%

\subsection{Notation}
Notation. Reminder to include rounding symbol

% 
% 8888888b.                  888      
% 888   Y88b                 888      
% 888    888                 888      
% 888   d88P 888d888 .d88b.  88888b.  
% 8888888P"  888P"  d88""88b 888 "88b 
% 888        888    888  888 888  888 
% 888        888    Y88..88P 888 d88P 
% 888        888     "Y88P"  88888P"  
%                                     
%                                     
%                                     
%

@@

\section{Private Localisation Preliminaries}
The localisation filter we introduce requires real-valued inputs and functions, and relies on a non-linear measurement model. We make use of an existing real-number encoding scheme which supports the homomorphic operations we'll require and an algebraic reformulation of the Extended Kalman Filter which reduces the filter update step to only use these operations.

% 
% ######## ##    ##  ######   #######  ########  #### ##    ##  ######   
% ##       ###   ## ##    ## ##     ## ##     ##  ##  ###   ## ##    ##  
% ##       ####  ## ##       ##     ## ##     ##  ##  ####  ## ##        
% ######   ## ## ## ##       ##     ## ##     ##  ##  ## ## ## ##   #### 
% ##       ##  #### ##       ##     ## ##     ##  ##  ##  #### ##    ##  
% ##       ##   ### ##    ## ##     ## ##     ##  ##  ##   ### ##    ##  
% ######## ##    ##  ######   #######  ########  #### ##    ##  ######   
%

\subsection{Integer Encoding for Real Numbers}

% TODO remove when not needed - for its simlicity, and applicability to our multiplication and bound requirements, is described in \cite{farokhiSecurePrivateControl2017}. It provides any number of homomorphic additions, and a predefined number of homomorphic multiplications.

In the encryption scheme introduced, weights and values are limited to integer values, and operations computed $\pmod{N}$ bound meaningful inputs to $x \in \mathbb{Z}_N$ for any weight or value $x$. The encoding scheme we have used

The encoding scheme is defined by the quantisation parameter $f$, representing the number of bits used to quantise the fractional part of a real number, and $N$ the modulus to use for handling negative numbers.

Encoding of a real number $a \in \mathbb{R}$ to an integer $e \in \mathbb{Z}$ is computed by
\begin{equation}
    e = \left\lfloor 2^{(m+1)f} a \right\rceil \pmod{N}\,,
\end{equation}
and decoding after $m$ homomorphic multiplications is computed by
\begin{equation}
    a = 
    \begin{dcases}
        \frac{e\hspace{-7pt}\pmod{N}}{2^{(m+1)f}}, &e\hspace{-7pt}\pmod{N} \leq \left\lfloor\frac{N}{2}\right\rfloor \\
        -\frac{N - e\hspace{-7pt}\pmod{N}}{2^{(m+1)f}}, &e\hspace{-7pt}\pmod{N} > \left\lfloor\frac{N}{2}\right\rfloor \\
    \end{dcases}\,.
\end{equation}

Note that adding encoding number to already encoded number requires the number of multiplications to be matched

that for the largest number of multiplications $m$, parameters for the encoding scheme when used with our ecncryption scheme should be defined such that
\begin{equation*}
    something \leq something\,else
\end{equation*}

encodings grow in size exponentially for each multilpication.

% 
% ######## #### ######## 
% ##        ##  ##       
% ##        ##  ##       
% ######    ##  ######   
% ##        ##  ##       
% ##        ##  ##       
% ######## #### ##       
%

@@

% 
% 8888888b.          d8b               888                       
% 888   Y88b         Y8P               888                       
% 888    888                           888                       
% 888   d88P 888d888 888 888  888      888      .d88b.   .d8888b 
% 8888888P"  888P"   888 888  888      888     d88""88b d88P"    
% 888        888     888 Y88  88P      888     888  888 888      
% 888        888     888  Y8bd8P       888     Y88..88P Y88b.    
% 888        888     888   Y88P        88888888 "Y88P"   "Y8888P 
%                                                                
%                                                                
%                                                                
%

@@

\subsection{Requirements for Measurement Model}
Must be such that Jacobian consists of linear combinations of state-related variables

@@

% 
% 8888888b.                            888 888             
% 888   Y88b                           888 888             
% 888    888                           888 888             
% 888   d88P .d88b.  .d8888b  888  888 888 888888 .d8888b  
% 8888888P" d8P  Y8b 88K      888  888 888 888    88K      
% 888 T88b  88888888 "Y8888b. 888  888 888 888    "Y8888b. 
% 888  T88b Y8b.          X88 Y88b 888 888 Y88b.       X88 
% 888   T88b "Y8888   88888P'  "Y88888 888  "Y888  88888P' 
%                                                          
%                                                          
%                                                          
%

@@

% 
%  .d8888b.                             
% d88P  Y88b                            
% 888    888                            
% 888         .d88b.  88888b.   .d8888b 
% 888        d88""88b 888 "88b d88P"    
% 888    888 888  888 888  888 888      
% Y88b  d88P Y88..88P 888  888 Y88b.    
%  "Y8888P"   "Y88P"  888  888  "Y8888P 
%                                       
%                                       
%                                       
%

@@

% Each appendix must have a short title.
% Sections and subsections are supported
% in the appendices.
\appendix
% 
%        d8888                                          888 d8b          
%       d88888                                          888 Y8P          
%      d88P888                                          888              
%     d88P 888 88888b.  88888b.   .d88b.  88888b.   .d88888 888 888  888 
%    d88P  888 888 "88b 888 "88b d8P  Y8b 888 "88b d88" 888 888 `Y8bd8P' 
%   d88P   888 888  888 888  888 88888888 888  888 888  888 888   X88K   
%  d8888888888 888 d88P 888 d88P Y8b.     888  888 Y88b 888 888 .d8""8b. 
% d88P     888 88888P"  88888P"   "Y8888  888  888  "Y88888 888 888  888 
%              888      888                                              
%              888      888                                              
%              888      888                                              
%

\section{Indistinguishability under Chosen Plaintext Attack (IND-CPA)} \label{app:ind_cpa}
A public-key encryption scheme is defined by the tuple of algorithms $(\mathsf{Setup}, \mathsf{Enc}, \mathsf{Dec})$, defined as
\begin{description}
    \item[$\mathsf{Setup}(\kappa)$] On input of security paramater $\kappa$, generate public key $pk$ and secret key $sk$
    \item[$\mathsf{Enc}(pk, x)$] Encryption of value $x$ is computable using the public key $pk$, obtaining $\mathcal{E}_{pk}(x)$.
    \item[$\mathsf{Dec}(sk, \mathcal{E}_{pk}(x))$] Decryption of value $x$ is computable using the secret key $sk$.
\end{description}
